\bf\mftitle

### 2011-03-01 doc/jInfer/basicigg/basicigg.tex
3187368 - Review documentation: cleanup - basic{rule,xsd,igg,dtd} done

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Matej Vitásek \\ \hline
Required tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.RuleDisplayer \\ \hline
Provided tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.IGGenerator \\ \hline
Module dependencies:   & Base \\ \hline
Public packages:       & cz.cuni.mff.ksi.jinfer.basicigg.properties \\ \hline
\end{tabular}

@@

One interesting use case for expansion is simple adaptation of legacy inference methods. "Old" methods working only with \emph{simple} grammar can be used unchanged with "new" inputs - schemas.\\

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer & Matej Vitásek \\ \hline
Required tokens       & \code{cz.cuni.mff.ksi.jinfer.base.interfaces.RuleDisplayer} \\ \hline
Provided tokens       & \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.IGGenerator} \\ \hline
Module dependencies   & Base \\ \hline
Public packages       & \code{cz.cuni.mff.ksi.jinfer.basicigg.properties} \\ \hline
\end{tabular}

@@

One interesting use case for expansion is simple adaptation of legacy inference methods. ``Old'' methods working only with \emph{simple} grammar can be used unchanged with ``new'' inputs - schemas.\\

### 2011-03-01 doc/jInfer/basicxsd/basicxsd.tex
3187368 - Review documentation: cleanup - basic{rule,xsd,igg,dtd} done

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Mário Mikula \\ \hline
Required tokens:       & none \\ \hline
Provided tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.SchemaGenerator \\ \hline
Module dependencies:   & Base \\ \hline
Public packages:       & none \\ \hline
\end{tabular}

@@

Named type of an element is defined by XSD element \code{simpleType} (lack of features mentioned above) or \code{complexType} with specified attribute \code{name}. Its content is exactly the same as described above. There is of course no need to define \emph{built-in types}.

@@

Default values for \code{minOccurs} and \code{maxOccurs} attributes are "1", if they are not specified. So the example above has the same meaning as the following one.

@@

Attributes are defined by XSD element \code{xs:attribute} with attributes \code{name}, \code{type} and optional \code{use}. Elements \code{xs:attributes} have to be placed at the end of a \code{complexType} definition.

@@

There are two classes extending \code{AbstractElementsExporter}. \code{GlobalElementsExporter} and \code{RootElementExporter}. Their constructors has the same signature as constructor of \code{AbstractElementsExporter} and both have \code{run()} method to perform their function.\\

@@

Name of a global type is derived from name of a corresponding global element by prefixing and suffixing it. Default prefix is "T" and default suffix is empty. These values can be changed in project properties.

\paragraph{Examples of definition of global types}
Type generated from element named "GlobalElement", containing elements "Text", which is string, and element "AnotherGlobalElement", which is another global element.

@@

Type generated from element named "X", containing element "Y", which is not global element and contains elements "Text" and "GlobalElement" from the previous example. Element "X" has one mandatory string attribute named "id".

@@

Global elements (retrieves from the result of preprocessing) are defined by referencing its type, which is supposed to be defined globally. This applies also to elements which are not global and their type is one of a built-in types. For example, root element "Root" contains one the following two elements. Global element "A" and string element "B".

@@

Elements which are not global and are not of a built-in type are defined recursively, at the place of their occurrence. For example, root element "Root" contains element "A", which contains two other string elements.

@@

Export of attributes is done alongside with export of elements, as attributes are exported as XSD element \code{xs:attribute} in XSD element \code{xs:complexType}.

@@

\subsection{"Unique Particle Attribution" problem}

@@

Flow of data in this module is the following.
\begin{enumerate}
	\item \code{Preprocessor} topologically sorts elements (rules) it got on input.
	\item For each element, its occurrence count is computed.
	\item Unused elements (occurrence count equals 0) are removed.
	\item For each element, it is determined if it type will be defined as a global type or not.
	\item For each global element, its type is exported to a XSD representation by \code{GlobalElementsExporter}.
	\item Root element and recursively all remaining elements are exported to a XSD representation by \code{RootElementExporter}.
	\item String representation of the schema is returned along with the information that file extension should be "xsd".
\end{enumerate}

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer & Mário Mikula \\ \hline
Required tokens       & none \\ \hline
Provided tokens       & \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.SchemaGenerator} \\ \hline
Module dependencies   & Base \\ \hline
Public packages       & none \\ \hline
\end{tabular}

@@

Named type of an element is defined by XSD element \code{simpleType} (lack of features mentioned above) or \code{complex\.Ty\.pe} with specified attribute \code{name}. Its content is exactly the same as described above. There is of course no need to define \emph{built-in types}.

@@

Default values for \code{minOccurs} and \code{maxOccurs} attributes are ``1'', if they are not specified. So the example above has the same meaning as the following one.

@@

Attributes are defined by XSD element \code{xs:\.attri\.bu\.te} with attributes \code{name}, \code{type} and optional \code{use}. Elements \code{xs:\.attri\.bu\.tes} have to be placed at the end of a \code{complexType} definition.

@@

There are two classes extending \code{AbstractElementsExporter}. \code{GlobalElementsExporter} and \code{Root\.Ele\.ment\.Ex\.port\.er}. Their constructors has the same signature as constructor of \code{AbstractElementsExporter} and both have \code{run()} method to perform their function.\\

@@

Name of a global type is derived from name of a corresponding global element by prefixing and suffixing it. Default prefix is ``T'' and default suffix is empty. These values can be changed in project properties.

\paragraph{Examples of definition of global types}
Type generated from element named ``GlobalElement'', containing elements ``Text'', which is string, and element ``AnotherGlobalElement'', which is another global element.

@@

Type generated from element named ``X'', containing element ``Y'', which is not global element and contains elements ``Text'' and ``GlobalElement'' from the previous example. Element ``X'' has' one mandatory string attribute named ``id''.

@@

Global elements (retrieves from the result of preprocessing) are defined by referencing its type, which is supposed to be defined globally. This applies also to elements which are not global and their type is one of a built-in types. For example, root element ``Root'' contains one the following two elements. Global element ``A'' and string element ``B''.

@@

Elements which are not global and are not of a built-in type are defined recursively, at the place of their occurrence. For example, root element ``Root'' contains element ``A'', which contains two other string elements.

@@

Export of attributes is done alongside with export of elements, as attributes are exported as XSD element \code{xs:\.attri\.bu\.te} in XSD element \code{xs:complexType}.

@@

\subsection{``Unique Particle Attribution'' problem}

@@

Flow of data in this module is the following.
\begin{enumerate}
	\item \code{Preprocessor} topologically sorts elements (rules) it got on input.
	\item For each element, its occurrence count is computed.
	\item Unused elements (occurrence count equals 0) are removed.
	\item For each element, it is determined if it type will be defined as a global type or not.
	\item For each global element, its type is exported to a XSD representation by \code{GlobalElementsExporter}.
	\item Root element and recursively all remaining elements are exported to a XSD representation by \code{Root\.Element\.Ex\.porter}.
	\item String representation of the schema is returned along with the information that file extension should be ``xsd''.
\end{enumerate}
